%  For credit to source, please look at the readme.txt file. 

%   We suggest to 
    %  Start all bullet item items with action verbs. You may base form or ing form or verbs where suited. See action verbs here, https://ecs.ihu.edu.gr/co/employment-cvcletter/action-verbs.html
    %  Provide the most relevant information
    %  Provide evidence for your skills.  For example, if you include MS Office and Python in your skills list, then provide bullet points detailing what YOU can do in MS Office and Python.  
    %  In each section--start entries with the most recent one
    %  Pay attention to grammar, avoid typos
    %  Avoid using abbreviations
    %  If you're applying for jobs, put your experience and skills before education
    %  Some examples of presentations are provided


    \documentclass[11pt]{article}

    \usepackage[T1]{fontenc}
    \usepackage{inter} 
    \renewcommand*\familydefault{\sfdefault}
    
    \usepackage{geometry}
    \geometry{
        a4paper,
        top=1.8cm,
        bottom=1in,
        left=2.5cm,
        right=2.5cm
    }
    
    \setcounter{secnumdepth}{0} % remove section numbering
    \pdfgentounicode=1 % make ATS friendly
    
    \usepackage{enumitem}
    \setlist[itemize]{
        noitemsep,
        left=2em
    }
    \setlist[description]{itemsep=0pt}
    \setlist[enumerate]{align=left}
    \usepackage[dvipsnames]{xcolor}
    \colorlet{icnclr}{gray}
    \usepackage{titlesec}
    \titlespacing{\subsection}{0pt}{*0}{*0}
    \titlespacing{\subsubsection}{0pt}{*0}{*0}
    \titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
    \titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
    \titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}
    
    \usepackage{xhfill} 
    \newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 
    
    \newif\ifRemVS % remove vspace between \section & \subsection
    \newcommand{\rvs}{
        \ifRemVS
            \vspace{-1.5ex}
        \fi
        \global\RemVSfalse
    }
    
    \usepackage{fontawesome5}
    
    \usepackage[bookmarks=false]{hyperref} % [imp!]
    \hypersetup{ 
        colorlinks=true,
        urlcolor=Sepia,
        pdftitle={My Resume},
    }
    
    \usepackage[page]{totalcount}
    \usepackage{fancyhdr}
    \pagestyle{fancy}
    \renewcommand{\headrulewidth}{0pt}	
    \fancyhf{}							
    
    \usepackage{amsmath}
    \usepackage{amsfonts}
    
    \begin{document}
    
    %== HEADER ==%
    \begin{center}      
        {\fontsize{28}{28}\selectfont Mircea Pop} \\ \bigskip
    
        {\color{icnclr}\faMapMarker} City, Country \quad 
        {\color{icnclr}\faEnvelope[regular]} \href{mailto:myaname@email.com}{myaname@email.com} \quad
        {\color{icnclr}\faIcon{mobile-alt}} \href{tel:+920000000000}{+92 000 0000000} 
        % You can also put your LinkedIn or website address
       % {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/}{linkedin.com/in/username}
    \end{center}
    %==============
    %==============
    %==============
    \section{About me}
    %==============
    %==============
    A summary of your goals and objectives...
    %==============
    %==============
    \section{Education}
    %==============
    %==============
    %==============
    %==============
    \subsection{Masters in Mathematics\hfill \normalfont 20XY}  
    
    \subsubsection{University of ABC,  City, Country}
    \begin{itemize}
        \item[\checkmark] \textit{GPA}: 3.8/4.0
        \item[\checkmark] \textit{Related coursework}: Mathematical modelling and numerical analysis
        \item[\checkmark] \textit{Thesis:} Write title of your thesis
        \end{itemize}
    %==============
    %==============
    \subsection{Bachelor Studies in Mathematics\hfill \normalfont 20XX}  
    
    \subsubsection{University of XYZ,  City, Country}
    \begin{itemize}
        \item[\checkmark] \textit{GPA}: 3.52/4.0
        \item[\checkmark] \textit{Related coursework}: Major in Mathematics with minor courses in Physics, Probability and Statistics
        \item[\checkmark] \textit{Thesis:} Write title of your thesis (if any)
        \end{itemize}
        
    %==============
    %==============
    \section{Research Projects}
    %==============
    %==============
    \subsection{Short and general version of most recent project's title} % This could be a short version of your master's thesis title
    \begin{itemize}
        \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z] 
        \item[\checkmark] Developed XYZ using ABC that led to X\% improvement 
        \item[\checkmark] Solved ABC with AAA method leading to CCC.
        \item[\checkmark] Accomplished XYZ feature to accomplish ABC.
        \item[\checkmark] Implemented XYZ library for ABC.
    \end{itemize}
    %==============
    %==============
    %==============
    \subsection{Short and general version of project's title} % This could be a short version of your bachelor's thesis title
    \begin{itemize}
        \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z] 
        \item[\checkmark] Developed XYZ using ABC that led to X\% improvement 
        \item[\checkmark] Solved ABC with AAA method leading to CCC.
        \item[\checkmark] Implemented XYZ library for ABC.
        \item[\checkmark] Utilized XYZ that increased AA by x\%
    \end{itemize}
    %==============
    %==============
    %==============
    %==============
    \section{Presentations}
    %==============
    %==============
    %==============
    % These are example presentations. Please replace all entries with your presentations. 
    %==============
    \begin{itemize}
    % Conference talks
        \item[\checkmark] Talk title, Conference name, City, Country (30 May 20XY)
        \item[\checkmark] Talk title, Conference name, City, Country (02 November 20XZ)
    % Class presentations
        \item[\checkmark] Presentation Topic in the course of XYZ, University of ABC, City, Country (03 November 20XY)
        \item[\checkmark] Euler method and modified Euler method in the course of Numerical Analysis, University of XYZ, City, Country (10 April 20XA)
    \end{itemize}
    %==============
    %==============
    \section{Skills}
    %==============
    %==============
    \subsection{Computational}
    \begin{itemize}
        \item[-] \textcolor{Sepia}{MATLAB}:
        \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z].  
        \item[\checkmark] Perfomed XYZ with ABC. 
        \item[\checkmark] Implemented XYZ library for ABC. 
        \item[-] \textcolor{Sepia}{Python}: 
        \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z].  
        \item[\checkmark] Perfomed XYZ with ABC. 
        \item[\checkmark] Implemented XYZ library for ABC.
    \end{itemize}
    \subsection{Problem Solving}
    \begin{itemize}
        \item[\checkmark] Investigated ....(complete these sentences or use another action verb)
        \item[\checkmark] Formulated .........
        \item[\checkmark] Coordinated ....
        \item[\checkmark] Created .........
        \item[\checkmark] Evaluated .........
    \end{itemize}
    \subsection{Typesetting}
    \begin{itemize}
        \item[-] \textcolor{Sepia}{\LaTeX}: 
        \item[\checkmark] Implemented XYZ method. 
        \item[\checkmark] Wrote CBA. 
        \item[\checkmark] Worked collaboratively on.... 
        \item[\checkmark] Created ....
        \item[-] \textcolor{Sepia}{MS Word}:  
        \item[\checkmark] Implemented XYZ method. 
        \item[\checkmark] Wrote CBA. 
        \item[\checkmark] Worked collaboratively on.... 
        \item[\checkmark] Created ....
    \end{itemize}
    \subsection{Languages}
    \begin{itemize}
        \item[-] \textcolor{Sepia}{Pashto}: Mother tongue
        \item[-] \textcolor{Sepia}{Urdu}: Second language
        \item[-] \textcolor{Sepia}{English}: Very good
            \item[\checkmark] IELTS: Reading--7, Writing--7.5, Speaking--6, Listening--6.
            \item[\checkmark] \textit{Writing:}  Demonstrated by my XYZ and......
            \item[\checkmark] \textit{Reading:}  Evident by my XYZ and......
            \item[\checkmark] \textit{Speaking and Listening:} Supported by my XYZ and.....
        \end{itemize}
    
    %==============
    %==============
    \section{Professional Qualification}
    %==============
    %==============
    \subsection{Bachelors of Education \hfill \normalfont 20XZ}
    \subsubsection{Open University,  City, Country }
    \begin{itemize}
        \item[\checkmark] \textit{Marks:} 80\% %\textit{}
        \item[\checkmark] \textit{Key Training:} Received training on ABC, XYZ and CCC
        \item[\checkmark] \textit{Thesis:} Completed a notable research project on [specific topic], contributing valuable insights to educational practices
    \end{itemize}
    
    \subsection{Diploma in Information Technology \hfill \normalfont 20XX}
    \subsubsection{Institute,  City, Country }
    \begin{itemize}
        \item[\checkmark] \textit{Marks:} 64.8\% %\textit{}
        \item[\checkmark] \textit{Key Training:} Received training on ABC, XYZ and CCC
        \item[\checkmark] \textit{Thesis:} Completed a notable project on [topic].
    \end{itemize}
    %==============
    %==============
    %==============
    %==============
    \section{Experience}
    %==============
    %==============
    \subsection{Private Maths Tutor \hfill \normalfont Feb 20XX -- July 20XY}
    \subsubsection{City, Country}
    % Start all items with action verbs
    \begin{itemize}
        \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z] 
        \item[\checkmark]  Developed XYZ using ABC that led to X\% improvement 
        \item[\checkmark] Solved ABC with AAA method leading to CCC.
        \item[\checkmark]  Accomplished XYZ feature to accomplish ABC.
        \item[\checkmark]  Implemented XYZ library for ABC.
    \end{itemize}
    
    \subsection{Role Name \hfill \normalfont Jan 20XX - Feb 20XY}
    \subsubsection{Company Name, City, Country}
    % Start all items with action verbs
    \begin{itemize}
        \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z] 
        \item[\checkmark]  Developed XYZ using ABC that led to X\% improvement 
        \item[\checkmark] Solved ABC with AAA method leading to CCC.
        \item[\checkmark]  Accomplished XYZ feature to accomplish ABC.
        \item[\checkmark]  Implemented XYZ library for ABC.
    \end{itemize}
    %==============
    %==============
    %==============
    %==============
    \section{Publications}
    %===========
    % Remove this section if you don't have any publications
    % replace with your publications, provide DOIs
    %==========
    \subsection{Journal Articles}
    \begin{itemize}
        \item[\checkmark] Authors-names in APA format. (20XY) Title of your publication. \textit{Journal Name}, \textbf{vol}(issue no): pages. DOI: 10.0000/j.jtbi.20XY.0000. % You may copy APA format from Google scholars
        \item[\checkmark] Ali, W., Overton, C.E., Wilkinson, R.R. \& Sharkey, K.J., (20XY) Deterministic epidemic models overestimate the basic reproduction number of observed outbreaks. \textit{Infectious Disease Modelling}, \textbf{9}(3):680–688. DOI: 10.1016/j.idm.20XY.02.007.
    \end{itemize}
    %===========
    %==========
    \subsection{Preprint(s)}
    \begin{itemize}
        \item[\checkmark] Morison, C., Fic, M., Marcou, T., Mohamadichamgavi, J., Antón, J. R., Sayyar, G., ... \& Ali, W. (20XY). Public Goods Games in Disease Evolution and Spread. arXiv preprint arXiv:2402.17842.
    \end{itemize}
    %===========
    %==========
    %==============
    %==============
    \section{Certifications \& Awards}
    %==============
    % Mentioned most important certificates where you have received some training or award or have delivered a presentation
    %==============
    \begin{itemize}
        \item[\checkmark] XYZ Scholarships
        \item[\checkmark] Received ABC Scholarship Award for the academic session 20XX-20XX
        \item[\checkmark] Certificate of Accomplishment, Awarding Body (28 Oct 20XZ)
        \item[\checkmark] Certificate of Merit in Masters (2019)
        \item[\checkmark] Certificate of Merit in Bachelors (2017)
    \end{itemize}
    %==============
    %==============
    %==============
    %==============
    \end{document}
    